---
title: "Graduate Bitcoin Project"
author: "Xu, Jin"
date: "11/28/2018"
output:
  pdf_document: default
  html_document: default
---

## 1. Data Preparations

```{r, echo = TRUE, eval = TRUE,message=FALSE}
library(zoo)
data <- read.table("BTC-USD-2013-2017.csv", sep=",", header=TRUE); attach(data) # original data
dates <- seq(as.Date('2013-01-01'), by = 'days', length = 1826) # transform to date formats
data$Date <- dates # append to original data
data <- read.zoo(data) # zoo formats
plot.zoo(data[,1], main = "BTC/USD", xlab = "Year", ylab = "Dollars")
plot.zoo(data, main = "all variables", xlab = "Year") 

```   

## 2. Bitcoin Data

### 2.1 Visualize Data

```{r, echo = TRUE, eval = TRUE,message=FALSE}

library(astsa);library(PerformanceAnalytics); library(evir);library(zoo)
bitcoin.logreturn <- diff(log(data[,1]))*100
bitcoin.logreturn.squared <- bitcoin.logreturn**2
par(mfrow=c(1,2))
plot.zoo(data[,1], main = "BTC/USD", xlab = "Year", ylab = "Dollars")
plot.zoo(bitcoin.logreturn, main = "BTC/USD Log Return", xlab = "Year")
par(mfrow=c(1,1))
acf(coredata(bitcoin.logreturn),lag.max = 200)
acf(coredata(bitcoin.logreturn**2), lag.max = 100);pacf(bitcoin.logreturn)

bitcoin.logreturn.squared <- bitcoin.logreturn**2


```

### 2.2 Check Normality

```{r, echo = TRUE, eval = TRUE,message=FALSE}

par(mfrow=c(1,2))
qqnorm(bitcoin.logreturn);qqline(bitcoin.logreturn)
hist(bitcoin.logreturn,main = "Histogram", xlab = "Return")

```

### 2.3 Fit an ARMA Model Using auto.arima

```{r, echo = TRUE, eval = TRUE,message=FALSE}

library(forecast)
auto.arima(bitcoin.logreturn, seasonal = FALSE, ic = "bic")

```

ARMA model: 
$$X_t = $$


### 2.4 Check Residuals of ARMA Model

```{r, echo = TRUE, eval = TRUE,message=FALSE}

library(astsa)
btc.logreturn.return <- sarima(bitcoin.logreturn, 3, 0, 2)
btc.logreturn.return

```

### 2.5 check residuals 

#### 2.5.1 Visualize Residuals and Squared Residuals

```{r, echo = TRUE, eval = TRUE, message=FALSE}

res.btc.logreturn.return <- resid(btc.logreturn.return$fit)
par(mfrow=c(2,2))
qqnorm(res.btc.logreturn.return);qqline(res.btc.logreturn.return);
hist(res.btc.logreturn.return); acf(res.btc.logreturn.return)
mtext("Residuals", side = 3, line =2, outer = TRUE)
res.square.btc.logreturn.return <- res.btc.logreturn.return**2
par(mfrow=c(1,2))
qqnorm(res.square.btc.logreturn.return);qqline(res.square.btc.logreturn.return);
acf(res.square.btc.logreturn.return,lag.max = 100)
#mtext("Squared Residuals ", side = 3, line =2, outer = TRUE)

```

#### 2.5.2 ARCH Engle's Test

```{r, echo = TRUE, eval = TRUE, message=FALSE}

library(aTSA)
arch.test(arima(bitcoin.logreturn, order = c(3,0,2)))

```

Therefore, squared residuals are heteroscedastic.



### Fit Garch Model

```{r, echo = TRUE, eval = TRUE, message=FALSE}
library(fGarch)
source("garchAuto.R")
#fit = garchAuto(bitcoin.logreturn, cores=8, trace=TRUE) ## can only work in MAC

btc.garch1 = garchFit(~arma(3,2)+garch(1,1), cond.dist = "std", data = bitcoin.logreturn, trace = FALSE, include.mean = FALSE)
btc.garch2 = garchFit(~arma(3,2)+garch(1,1), cond.dist = "sstd", data = bitcoin.logreturn, trace = FALSE, include.mean = FALSE)
summary(btc.garch1)
summary(btc.garch2)

btc.garch3 = garchFit(~garch(1,1), cond.dist = "std", data = bitcoin.logreturn, trace = FALSE, include.mean = FALSE)
btc.garch4 = garchFit(~garch(1,1), cond.dist = "sstd", data = bitcoin.logreturn, trace = FALSE, include.mean = FALSE)
summary(btc.garch3)
summary(btc.garch4)

btc.garch5 = garchFit(~arma(1,3)+garch(1,1), cond.dist = "std", data = bitcoin.logreturn, trace = FALSE, include.mean = FALSE)
btc.garch6 = garchFit(~arma(1,3)+garch(1,1), cond.dist = "sstd", data = bitcoin.logreturn, trace = FALSE, include.mean = FALSE)
summary(btc.garch5)
summary(btc.garch6)


#btc.garch1.res=btc.garch1@residuals	# residuals time series
#btc.garcho.res=btc.garcho@residuals	# residuals time series
#acf(btc.garch1.res); acf(btc.garch1.res**2)
#acf(btc.garcho.res); acf(btc.garcho.res**2)

```

```{r, echo = TRUE, eval = TRUE, message=FALSE}
par(mfrow=c(2,1))
btc.garch5.res=btc.garch5@residuals	# residuals time series
acf(btc.garch5.res,lag.max = 100); acf(btc.garch5.res**2,lag.max = 100)

```

```{r, echo = TRUE, eval = TRUE, message=FALSE}
btc.garch5.pred=predict(btc.garch5,n.ahead=300,trace=F, plot = TRUE)

```

### Literature Review of Univariate Garch model



## Data Manipulation

### NA data equals previous day

```{r, echo = TRUE, eval = TRUE,message=FALSE}
library(timeSeries)
# Equal non-existent data to previous day's
data.previous <- interpNA(data, method = "before")
# calculate log return
dataset.log.previous <- na.trim(diff(log(data.previous)))
plot.zoo(dataset.log.previous, main = "Returns with NA data Equaling Previous Day")
```

### CCF

```{r, echo = TRUE, eval = TRUE,message=FALSE}
for (m in (2:ncol(dataset.log.previous))) {
  ccfvalues <- ccf(dataset.log.previous[,m], dataset.log.previous[,1])
  ccfvalues
  lag2.plot(dataset.log.previous[,1], dataset.log.previous[,m],10)
}
```


### Remove row with NA

```{r, echo = TRUE, eval = TRUE,message=FALSE}
library(timeSeries)
# remove rows with non-existent data
data.complete <- removeNA(data)
# calculate log return
dataset.log.complete <- removeNA(diff(log(data.complete)))
plot.zoo(dataset.log.complete, main = "Returns with NA Data Removed")
```



### fit model

$$X_t = \beta'z_t+y_t^* = \beta_1 Fed_{t-1} +  \beta_2 EURUSD_{t-1} + \beta_3 DJI_{t-1} + \beta_4 Gold_{t-1} + \beta_5 Oil_{t-1} + \beta_6 RUT_{t-1} + \beta_7 GSPC_{t-1} + \beta_8 EEM_{t-1}$$

$$\phi(B) y_t^* = \theta(B) y_t$$
or

$$y_t^* = \beta_0 + \beta_1 y_{t-1} + \beta_2 y_{t-2}$$

$$y_t = \sigma_t \epsilon_t$$

$$\sigma_t^2 = \alpha_0 + \sum_{j=1}^m{\alpha_j}y_{t-j}^2 + \sum_{j=1}^s{\beta_j}\sigma_{t-j}^2=\alpha_0+\alpha y_{t-1}^2 + \beta \sigma_{t-1}^2$$

```{r, echo = TRUE, eval = FALSE,message=FALSE}
dlp <- as.data.frame(dataset.log.previous) 

library(dplyr); library(knitr)

modeldata <- mutate(dlp, z1 = lag(Federal.Rate,7),z2 = lag(EURUSD,2), z3 = lag(DJI,6),z4 = lag(Gold,5),z5 = lag(Crude.Oil,7),z6 = lag(RUT,6),z7 = lag(GSPC,6),z8 = lag(EEM,9))
modeldata1 <- modeldata %>% select(Adj.Close,z1, z2, z3, z4, z5, z6, z7, z8)

modelfit <- lm(Adj.Close ~ ., data = modeldata1)
summary(modelfit)

```
```{r, echo = TRUE, eval = FALSE,message=FALSE}
res <- modelfit$residuals
par(mfrow=c(1,2))
qqnorm(res);qqline(res);acf(res)

```
```{r, echo = TRUE, eval = FALSE,message=FALSE}
auto.arima(res, seasonal = FALSE, ic = "bic")
resarma <- sarima(res, 3, 0, 2)
```
```{r, echo = TRUE, eval = FALSE,message=FALSE}
resss <- resid(resarma$fit)
par(mfrow=c(2,1))
acf(resss);acf(resss**2,lag.max = 100)
```

```{r, echo = TRUE, eval = FALSE,message=FALSE}
source("garchAuto.R")
fit1 = garchAuto(res, cores=8, trace=TRUE) ## can only work in MAC
fit1
```

```{r, echo = TRUE, eval = FALSE,message=FALSE}
res.garch5 = garchFit(~arma(1,3)+garch(1,1), cond.dist = "std", data = res, trace = FALSE, include.mean = FALSE)

par(mfrow=c(2,1))
res.garch5.res=res.garch5@residuals	# residuals time series
acf(res.garch5.res,lag.max = 100); acf(res.garch5.res**2,lag.max = 100)

```